### 2017-02-21 Manuscript/SW_early_life_telomeres.Rmd
Edits

4. Telomere length and the slope of the relationship with age varied markedly among cohorts. Telomere length was positively associated with island-wide temporal insect abundance - a key resource for the insectivorous Seychelles warbler - suggesting that the costs associated with living in harsher environments can be studied by investigating telomere dynamics. We also found evidence for sex-specific relationships between telomeres and tarsus length, potentially reflecting differential costs of growth.

@@

###Introduction
A major aim of ecologists and evolutionary biologists is to quantify and understand why individuals vary in their response to different environmental factors. Identifying this variation in environmental costs is central to understanding variation in fitness [@Lindstrom1999], and thus for understanding population and community dynamics [@Bolnick2011]. Furthermore, knowledge of the relative impact that different environmental factors exert on individuals, and why individuals may differ in mitigating these costs, is important to understanding evolutionary trade-offs and life-history strategies [@Stearns1992]. However, fully quantifying individual-level variation in costs is impossible in wild systems, and thus effective biomarkers that reflect the physiological consequences of individual-level experiences are required.

>>>>

4. Telomere length and the slope of the relationship with age varied markedly among cohorts. Telomere length was positively associated with temporal variation in island-wide insect abundance - a key resource for the insectivorous Seychelles warbler - suggesting that the costs associated with living in harsher environments can be studied by investigating telomere dynamics. We also found evidence for sex-specific relationships between telomeres and tarsus length, potentially reflecting differential costs of growth.

@@

###Introduction
A major aim of ecologists and evolutionary biologists is to understand why individuals vary in their response to different environmental factors. Identifying this variation in environmental costs is central to understanding variation in fitness [@Lindstrom1999], and thus for understanding population and community dynamics [@Bolnick2011]. Furthermore, knowledge of the relative impact that different environmental factors exert on individuals, and why individuals may differ in mitigating these costs, is important to understanding evolutionary trade-offs and life-history strategies [@Stearns1992]. However, fully quantifying individual-level variation in costs is impossible in wild systems, and thus effective biomarkers that reflect the physiological consequences of individual-level experiences are required.
